% Experience
\newcommand{\cvexperiencesetion}{%
\cvsection{Professional Experience}
\cvexperience{Project Portfolio Manager}{https://company1.example.com/}{Company 1}{Region A, Region B}{Dec. 2021}{Dec. 2024}{%
\begin{itemize}
    \item Accomplished a successful integration of generative AI capabilities into existing projects, resulting in 90\% improvement in reporting time by spearheading the implementation.
    \item Increased project delivery efficiency by 10\% across the organisation as measured by a backlog health indicator by establishing and scaling a PMO, implementing best practices and Agile methodologies.
    \item Improved focus on high-value initiatives by 80\% as measured by the backlog size by implementing data-driven prioritisation methods, KPIs and building comprehensive dashboards.
    \item Mentored and developed newcomers fostering a culture of continuous improvement and accountability.
\end{itemize}}

\cvexperience{Project Manager}{https://company2.example.com/}{Company 2}{Region C, Region D, Region E}{Mar. 2019}{Nov. 2021}{%
\begin{itemize}
    \item Successfully managed 3 complex, multidisciplinary projects in the transportation sector across 5 countries, resulting in 5 star reviews from customers.
    \item Improved project delivery time and team collaboration efficiency by implementing Agile methodologies.
    \item Increased project profitability by 15\% by successfully negotiating out-of-scope work and managing all financial aspects.
    \item Enhanced stakeholder satisfaction by organising weekly workshops as measured and maintaining strong relationships with key stakeholders across numerous organisations.
\end{itemize}}

\cvexperience{Systems Design Engineer}{https://company3.example.com/}{Company 3}{Region F}{Jan. 2018}{Feb. 2019}{%
\begin{itemize}
    \item Incrementally improved performance and reliability of SaaS systems across 5 railway projects by spearheading critical product enhancements.
    \item Accomplished the successful integration of dozens new real-time system features as measured by the monthly releases by leading cross-functional collaborations with suppliers and RAMS teams.
    \item Increased efficiency in resolving complex technical issues by 20\% as measured by automating tasks and serving as the primary liaison between engineering, product management, and client-facing teams.
    \item Contributed to numerous project quotations and proposals by providing strategic insights, enhancing the company's competitive position in the market.
\end{itemize}}

\cvexperience{Solution Architect}{https://company4.example.com/}{Company 4}{Region G, Region H}{Jan. 2017}{Dec. 2017}{%
\begin{itemize}
    \item Accelerated time-to-market for new features by 30\% by implementing agile methodologies to improve development efficiency.
    \item Increased successful bids by 25\% by collaborating closely with sales and engineering teams to develop compelling proposals.
    \item Accomplished a seamless transition from legacy systems to innovative product versions, resulting in no operational disruptions by orchestrating the product roadmap and ensuring timely delivery.
    \item Improved product development and change management by introducing robust and lightweight processes.
\end{itemize}}

\cvexperience{Solution Manager}{https://company5.example.com/}{Company 5}{Region I}{Oct. 2013}{Dec. 2016}{%
\begin{itemize}
    \item Increased project profitability by 15\% across the department by managing an average of 7 concurrent projects using Agile SCRUM methodologies.
    \item Supported a couple of multi-million euro proposals, resulting in detailed solutions to increase department revenue by demonstrating expertise in risk management, financial planning, and resource allocation.
    \item Improved client insights and decision-making by 10-30\% as measured by success rates KPIs by developing and marketing innovative IT, Cloud, Data Analytics, and Embedded Systems solutions.
\end{itemize}}

\cvexperience{Validation Manager}{https://company6.example.com/}{Company 6}{Region J, Region K}{Sep. 2008}{Sep. 2013}{%
\begin{itemize}
    \item Improved validation efficiency by 60\% by developing a SOTA real-time HIL simulator and expanding its application across 3 product lines.
    \item Accomplished 15\% improvement in inter-departmental collaboration as measured by higher output quality by establishing and leading the Validation Department, implementing robust processes for requirements management and gap analysis.
    \item Enhanced team performance by 30\% as measured by the testing time by recruiting, training, and managing a team of 5 validation engineers, instilling a culture of excellence and continuous improvement.
\end{itemize}}

\cvexperience{Software Development Manager}{https://company7.example.com/}{Company 7}{Region L, Region M, Region N, Region O}{Dec. 2000}{Aug. 2008}{%
\begin{itemize}
    \item Recovered a 6-month delay on a critical project by leading a task force, resulting in improvements in projects’ timeline adherence.
    \item Reduced time-to-market by 40\% and improved overall product quality by 10\% as measured by the time-to-ship and QA reports by establishing automated processes for delivery, testing, reporting, and configuration management.
    \item Successfully delivered 8 key real-time and mission-critical modules for worldwide clients, resulting in hundreds of released new features.
    \item Improved team efficiency by mentoring junior team members and facilitating knowledge transfer initiatives.
\end{itemize}}
}