% Projects
\newcommand{\cvprojectssection}{%
\cvsection{Projects}
\begin{itemize}
    \item Python - 2024 - now
    \begin{itemize}
        \item PM Assistant
        \begin{itemize}
            \item AI application to gather project context, history and latest updates for reports.
            \item Tools and Technologies
            \begin{itemize}
                \item RAG
                \item Multimodal
                \item Azure DevOps API
                \item Ollama API
                \item OCR
                \item Streamlit
            \end{itemize}
        \end{itemize}

        \item Timesheets synchronisation
        \begin{itemize}
            \item Application for synchronising ERP timesheets with ticketing systems.
            \item Tools and Technologies
            \begin{itemize}
                \item Odoo API
                \item Azure DevOps and Gitea APIs
                \item Streamlit
            \end{itemize}
        \end{itemize}

        \item Web Scrapper
        \begin{itemize}
            \item Search engines: Brave, Google, DuckDuckGo and Yandex
            \begin{itemize}
                \item Text to text
                \item Text to image
                \item Image to image
            \end{itemize}
            \item Link depth control
            \item Data extraction with beautiful soup
            \item OCR
        \end{itemize}
    \end{itemize}
    
    \item SwiftUI
    \begin{itemize}
        \item The apps below are Apple Health compatible, integrate APIs, have iPhone, Apple Watch and iPad compatibility.
        \item \href{https://example.com/app1}{\textbf{App 1}} : Health tracking app with scheduling, workouts, barcode scanning, history and analysis features. - 2020 to now
        \item \href{https://example.com/app2}{\textbf{App 2}}: Sports performance tracker with game history, metrics counter and analysis features. - 2024 to now
    \end{itemize}

    \item Power Automate
    \begin{itemize}
        \item Flow to automatically calculate projects' relative priority adapted from SAFe methodology. Triggered by the creation of new projects in Azure DevOps. - 2023
        \item Flow to calculate the backlog health KPI on a daily basis, keep track of the KPIs history and publish it to stakeholders. - 2024
        \item Flow to publish the high priority tickets in need of attention to the appropriate team(s). - 2023
        \item Flow to create a daily report of tickets created during UAT for follow up by POs. - 2024
    \end{itemize}

    \item Power App
    \begin{itemize}
        \item App - 2019
        \begin{itemize}
            \item record meetings' to OneNote
            \item create and assign actions in ToDo
            \item send email with notes and actions
            \item setup follow up reminders
        \end{itemize}
    \end{itemize}

    \item Others
    \begin{itemize}
        \item Mailcow on Linux VPS with SPF, DKIM and DMARC.
        \item NextCloud on Linux VPS
        \item Home Assistant on Raspberry Pi 4 with Zigbee, ZigWave, Shelly, SmartThings, Matter, etc.
        \item Synology NAS - Docker
        \begin{itemize}
            \item WordPress website with Cloudflare - 2024 to now
            \item React website with Cloudflare - 2025 to now
            \item GitLab server - 2024 to now
            \item n8n server - 2023 to now
            \item Pi-hole - 2022 to now
            \item Minecraft server - 2022 to now
            \item Portainer - 2022 to now
            \item Watchtower - 2022
            \item Focalboard - 2024
            \item Paperless - 2024
            \item VPN - 2024
            \item Login container with JWT to redirect to AI server running on Ollama - 2024
        \end{itemize}
    \end{itemize}

    \item Lua (Games) - 2019
    \begin{itemize}
        \item Zelda
        \item Flappy Bird
        \item Zombie Arena
        \item Breakout
        \item Match3
        \item Mario
        \item Pong
        \item Angry Birds
    \end{itemize}

    \item C\# (Games) - 2019
    \begin{itemize}
        \item Timber
        \item Super Zombie Runner
    \end{itemize}

    \item VBA
    \begin{itemize}
        \item Macro to reformat Word document, generate PDF and attach it to template email for distribution to stakeholders. - 2021
        \item Macro to scan for errors, clean and reformat Excel file that was published to calculate real time system delays. - 2019
        \item Macro to extract timesheet information from all team members to generate report on the efforts per project for upper mangement. - 2008
        \item Macro with state machine to select NTP servers on a network and update time on local machine. - 2005
    \end{itemize}

    \item LabView
    \begin{itemize}
        \item Real time state of the art train simulator - 2008 - 2013
        \begin{itemize}
            \item Used LavView FPGA to implement real time floating point operations
            \item Train engine simulation state machine with 1 microssecond period
            \item Integrated with CAN, RS232 and SPI protocols
            \item Integrated with DLLs for access to embedded data
            \item Automatic testing, data download and pass/fail analysis
            \item Hands free testing and reports
            \item Integrated with TestStand
        \end{itemize}
    \end{itemize}

    \item batch
    \begin{itemize}
        \item Script to build package with all modules' DLLs and Scada to create setup executable for distribution. - 2007
        \item Script to retrieve latest code from ClearQuest, compile all modules and publish the release for different Scada target versions. - 2006
    \end{itemize}

    \item C/C++
    \begin{itemize}
        \item Genetic Programming - 2000
        \begin{itemize}
            \item Trains Operation Control Center using SCADA and FrontVue
            \item Wall following robot
            \item Ball following robot
        \end{itemize}
        \item Optical Flow - 2002 - 2004
        \begin{itemize}
            \item Trains Platform Monitoring using Optical Flow
        \end{itemize}
    \end{itemize}
\end{itemize}
}